\documentclass{article}

\usepackage{todonotes}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{enumerate}
\usepackage{caption}
\usepackage{subcaption}

\begin{document}
\section{About this minor change}

\subsection{Why I wrote it}
I wrote this Minor Change, because I could not find any Pilatus B4 gliders with a documented installation of a transponder. With lots of support from many gliding friends, I wrote the document. Thanks! It was sent by EASA to the Dutch authorities, who asked me to specify which transponders and antennae the Minor Change should apply to. After I supplied a list, the Minor Change was approved.

\subsection{Usage}
Everybody who wants to use this minor change, may do so. Feel free to spread the complete PDF, including this page, any way you like as long as it’s free of charge. I intend to spread the document to Pilatus, EWMS, Garrecht, Funkwerk, and a bunch of newsgroups/forums/etc I know of. 

Using this minor change does not cost you anything. Applying for this minor change cost me 290 euros (which I had to pay to EASA), plus many hours creating the document, sending it, and corresponding to questions. 
Therefore, you are welcome to contact me, should you wish to compensate me for my efforts. Also, you are encouraged to share your work as well.

\subsection{Technical note}
Please mind the risk of contact-corrosion when installing the antenna. The copper can cause contact-corrosion with the aluminum skin of the glider. 

\subsection{Expanding}
Should you want to expand upon this Minor Change, then you can grab the source document (written in LaTeX, built using “make” on Linux), change what you like and apply for a new minor change at EASA. Applying at EASA will cost you the full 290 euros I’m afraid.
The complete source is available here: \href{https://github.com/roeles/minor_change_transponder}.
Naturally I am also willing to help you convert this document into other formats for editing.

\subsection{Contact}
Should you have any questions, feel free to contact me. \\
\\
Roel Baardman \\
\href{mailto:roel.baardman@gmail.com}{roel.baardman@gmail.com}

\newpage
This page is intentionally left blank.
\end{document}
